---
title: "Neural Networks"
author: "Zach Diener"
date: "June 1, 2015"
output: html_document
---

I will be construction a function to model the network shown in the slides(pg 60). 

#Define Inputs
```{r}
L=list(x=0:4, y=0:4) 
  
 
```
 

#Construction of The Function
```{r}

 f=function(x,y) {(matrix(c(0.5,1,1.5),1,3) %*% tanh(matrix(c(-3,-2,-1,3,3,-1),3,2,byrow=T) %*% matrix(c(x,y),2,1)+ matrix(c(6,-6,-3),3,1)))+3}
 
```

#Execute Code
```{r}
mapply(f,L$x,L$y)
```
This function will first take x,y inputs and multiply them by the 3 by 2 matrix of scalars for the first iteration of the network. Then the 3 by 1 matrix will be added to account for the bias. From here the exponential tangent function is appplied. This result is then multiplied by the 1 by 3 matrix of scalars corresponding to the second iteration of the network. Final a bias of three is added to the result above. 
#Plotting the Data
```{r}
 x=c(.1,.15,.2,.3,.5,.8)
 y=c(.6,.65,.8,1.3,1.5,1.4)
 
 x_1=c(.8,1.1,1.2,1.7,1.9)
 y_1=c(2.8,2.9,3.3,3.4,3.5)
 
 x_2=c(2.1,2.4,2.8,2.8)
 y_2=c(1.3,1.9,2.2,2.4)
 
 
 plot (x,y, col="red", xlim=c(0,4),ylim=c(0,4))
 points(x_1,y_1, col="blue")
 points(x_2,y_2, col="green")
 
 abline(5,-3)
 abline(-3,3)
 abline(2,.3333)
``` 
This will allow for the data to be plotted as three seperate groupings. Then they may be seperated by color. From here I plotted three lines to seperate the groups of data. This is not apperent in my graph however due to the random generation of my data (see a,b,c=rnorm(5)).