---
title: "Neural Networks"
author: "Zach Diener"
date: "June 1, 2015"
output: html_document
---

I will be constructing a function to model the network shown in the slides(pg 60). 

#Define Inputs
```{r}
L=list(x=0:4, y=0:4) 
  
 
```
 

#Construction of The Function
```{r}

 f=function(x,y) {(matrix(c(0.5,1,1.5),1,3) %*% tanh(matrix(c(-3,-2,-1,3,3,-1),3,2,byrow=T) %*% matrix(c(x,y),2,1)+ matrix(c(6,-6,-3),3,1)))+3}
 
```

#Execute Code
```{r}
mapply(f,L$x,L$y)
```
This function will first take x,y inputs and multiply them by the 3 by 2 matrix of scalars for the first iteration of the network. Then the 3 by 1 matrix will be added to account for the bias. From here the exponential tangent function is appplied. This result is then multiplied by the 1 by 3 matrix of scalars corresponding to the second iteration of the network. Final a bias of three is added to the result above. 
#Plotting the Data
```{r}
 x=c(0.20,0.54,0.32,0.40,0.70,0.70)  
y=c(1.42,1.42,0.82,0.52,1.16,0.78)   
  
x_1=c(1.74,1.82,1.22,0.78,1.28)        
y_1=c(2.82,3.38,3.58,3.40,2.76)       
  
x_2=c(2.10,2.44,2.72,2.72)            
y_2=c(2.36,2.20,1.84,1.36)
 
 
 plot (x,y, col="red", xlim=c(0,4),ylim=c(0,4))
 points(x_1,y_1, col="blue")
 points(x_2,y_2, col="green")
 
 abline(5,-3)
 abline(-3,3)
 abline(2,.3333)
``` 
This will allow for the data to be plotted as three seperate groupings. Then they may be seperated by color. From here I plotted three lines to seperate the groups of data. 
